---
title: "Incarceration Analysis"
author: "Busung Chung"
date: '2022-11-01'
output: html_document
---

```{r echo=FALSE, eval=TRUE, message=FALSE}
source("../source/a4-helpers.R")
source("../source/analysis.R")
```

## Abstract 
The incarceration rates have been rising as significantly as time passed by. The changes in law and policies introduced to the public has a direct implication to confinement in jail. Gender and racial backgrounds have a crucial in identifying the problem to the system. 

# Test (TODO: Remove before submission!!)
```{r echo=FALSE}
q1_string <- test_query1()
num <- 5
```
As you know, this is a markdown report. The [R Markdown Cheatsheet](https://www.rstudio.com/wp-content/uploads/2015/02/rmarkdown-cheatsheet.pdf) is **useful!**

* Here's a test of a dynamic variable. Say **"`r q1_string`!!!** 
* Here's another test. A vector
of numbers: `r test_query2(num)`.

Recall that _{r echo=TRUE}_ can be used to display the code, 
which is very useful when developing and debugging a report. Here's an example: 

```{r echo=TRUE}
num <- 5
sum <- sum(test_query2(num))
print(sum)
```

## Introduction 
Incarceration rates have increased over the years leading to a high volume of individuals going in and out of prison frequently. This might be due to modifications of regulations that directly influence whether a individual is going to jail or not. Through the dataset provided by VERA, I was able to accumulate different graphs for further analysis. 

## Data Summary 
[TODO]

[TODO ... other sections ... See Canvas for details]

_All the very best with your work!_

